Extending Morphological Chains with Supervised Learning and Cross-Language Features

### 2015-12-10 paper/paper.tex
paper

% TODO explain existing code
\section{Introduction}
Morphologically related words\dots %%TODO

@@

explanation blah
%TODO better explanation

@@

We used the datasets provided by 2010 Morpho Challenges. For English, this includes
a wordlist with word frequencies of approximately 878,000 words scraped from the
Wortschatz collection from the University of Leipzig, CLEF, and the Europarl corpus
as well as gold standard segmentation training and development sets of approximately 
1000 randomly selected words. Gold standard segmentation is based on the CELEX database.
For Turkish, the word list contains approximately 670,000 words, with gold standards
from a morphological parser developed at Boğaziçi University. The Turkish wordlist
was obtained from a significantly smaller corpus --- at 1 million words, compared
to the English corpus of 18 million.

We tested on 4 different sizes of wordvectors:
of wordvector 
small is 2.5k
med is 
large is 160k
full is 878k

@@

\begin{table*}
    \begin{center}
        \begin{tabular}{ | l | l | l | l | l |}
            \hline
            Language & Method & Precision & Recall & F1 \\ \hline
                     & Narasimhan & 0.807 & 0.722 & 0.762 \\ 
                     & Unsupervised & -  & - & - \\ 
            English & Semi-supervised & - & - & - \\ 
                    & Two language unsupervised & - & - & - \\ 
                    & Two language semi-supervised & - & - & - \\ \hline
                    & Narasimhan & 0.743 & 0.520 & 0.612 \\ 
                    & Unsupervised & - & - & - \\ 
            Turkish & Semi-supervised & - & - & -  \\ 
                    & Two language unsupervised  & - & - & -  \\ 
                    & Two language semi-supervised  & - & - & -  \\ \hline
        \end{tabular}
        \caption{Results 'n shit TODO}
    \end{center}
\end{table*}

\begin{table*}
    \begin{center}
        \begin{tabular}{ | l | l | l | l | l | l |}
            \hline
            Language & \multicolumn{2}{|c|}{\textbf{Correct Segmentations}} & \multicolumn{3}{|c|}{\textbf{Incorrect Segmentations}}\\ \hline
                     & Word & Segmentation & Word & Predicted & Correct\\ \hline
            English & suburbanite & suburb/an/ite & provokingly & provok/ing/ly & provoking/ly  \\ 
                    & buffeted & buffeted & -  & - & -\\ 
                    & ewers' &  ewer/s/' & - & - & -\\ 
                    & yowling & yowl/ing & - & -& - \\ 
                    & Two language semi-supervised & - & - & - & -\\ \hline
                    & Narasimhan & 0.743 & 0.520 & 0.612 & -\\ 
                    & Unsupervised & - & - & - & -\\ 
            Turkish & Semi-supervised & - & - & -  & -\\ 
                    & Two language unsupervised  & - & - & -  & -\\ 
                    & Two language semi-supervised  & - & - & -  & -\\ \hline
        \end{tabular}
        \caption{Results 'n shit TODO}
    \end{center}
\end{table*}

>>>>

% TODO explain existing code
\section{Introduction}
The division of a word into morphemes--basic units of meaning--- encodes information about
something
When performing morphological analysis, there are a few different cases to consider: words that share similar
meaning but appear in diffrent syntactic contexts (``German" ---``Germanic"), new words generated from
the combination of two separate words (``bookcase"|``book"---``case"), words with dissimilar meaning but
derived from one another ``insuffcient"---``sufficient"). In the first and last case, words are often related
by the addition of preffixes, suffixes, and other affixes. This allows us to form morphological chains - which
link a base word to its derivative through a series of affixations.
We wish to

%%TODO

@@

We want to maximize the probability of the document $D$, where $w$ is a word in $D$ and $c$ is
its segmentation. As above, we 
%TODO better explanation

@@

We used the datasets provided by 2010 Morpho Challenges. For English, this includes
a wordlist with word frequencies of approximately 878,000 words scraped from the
Wortschatz collection from the University of Leipzig, CLEF, and the Europarl corpus
as well as gold standard segmentation training and development sets of approximately 
1000 randomly selected words. Gold standard segmentation is based on the CELEX database.
For Turkish, the word list contains approximately 670,000 words, with gold standards
from a morphological parser developed at Boğaziçi University. The Turkish wordlist
was obtained from a significantly smaller corpus -- at 1 million words, as compared
to an English corpus of 18 million.

We tested on 4 different sizes 
of wordvector 
small is 2.5k
med is 
large is 160k
full is 878k

@@

\begin{center}
    \begin{tabular}{ | l | l | l | l | l |}
    \hline
    Language & Method & Precision & Recall & F1 \\ \hline
      & Narasimhan & 0.807 & 0.722 & 0.762 \\ 
    & Unsupervised & -  & - & - \\ 
    English & Semi-supervised & - & - & - \\ 
     & Two language unsupervised & - & - & - \\ 
     & Two language semi-supervised & - & - & - \\ \hline
     & Narasimhan & 0.743 & 0.520 & 0.612 \\ 
    & Unsupervised & - & - & - \\ 
    Turkish & Semi-supervised & - & - & -  \\ 
     & Two language unsupervised  & - & - & -  \\ 
     & Two language semi-supervised  & - & - & -  \\ \hline
    \end{tabular}
\end{center}

\begin{center}
    \begin{tabular}{ | l | l | l | l | l | l |}
    \hline
    Language & \multicolumn{2}{|c|}{\textbf{Correct Segmentations}} & \multicolumn{3}{|c|}{\textbf{Incorrect Segmentations}}\\ \hline
     & Word & Segmentation & Word & Predicted & Correct\\ \hline
    & 'suburbanite' & 'suburb/an/ite' & 'provokingly' & 'provok/ing/ly' & 'provoking/ly'  \\ 
    'buffeted' & 'buffeted' & -  & - & - & -\\ 
    "ewers'" &  "ewer/s/'" & - & - & - & -\\ 
    'yowling' & 'yowl/ing' & - & - & -& - \\ 
     & Two language semi-supervised & - & - & - & -\\ \hline
     & Narasimhan & 0.743 & 0.520 & 0.612 & -\\ 
    & Unsupervised & - & - & - & -\\ 
    Turkish & Semi-supervised & - & - & -  & -\\ 
     & Two language unsupervised  & - & - & -  & -\\ 
     & Two language semi-supervised  & - & - & -  & -\\ \hline
    \end{tabular}
\end{center}
